Reference Tracking Strategies of Deaf Adult Signers in Turkish Sign Language

### 2023-05-01 revised_manuscript.Rmd
updated

However, this particular observation is not peculiar to spoken languages. There is an emerging body of literature that reports the distribution of REs in signed narratives [@czubek2017; @ferrara2022; @swabey2002; @frederiksen2016; @perniss2015; @morgan2005; @hodge2019; @ahlgren1994]. Building on the work by @gundel1993, @swabey2002 demonstrated that, like other languages such as Russian, Chinese, and Japanese, American Sign Language (ASL) signers use bare nouns for introduced and re-introduced discourse contexts whereas zero anaphora is used for referents which are "in-focus" or very accessible to the addressee. Overt REs like pronouns or nouns are disprefered for such referents. @swabey2002 concluded that "native" signers in her study abided by the Gricean maxim of quantity and thus used more economic forms of reference tracking. Similar findings have been reported for German Sign Language (Deutsche Gebärdensprache - DGS) [@perniss2015] and British Sign Language (BSL) [@morgan2005]. It is important to note, however, that this research either collapsed DoD and DoH signers into a single group and labeled them as "native-like" or explicitly compared native deaf signers with late deaf signers (with delayed exposure to a sign language) in terms of narrative competence. Most recently, @ferrara2022 examined corpora including video-recorded narratives from five different sign languages including Irish Sign Language, Finnish Sign Language, Norwegian Sign Language and Swedish Sign Language and investigated how these languages established and maintained referents. Like other observations, this research showed that, across each of these languages, bare nouns were used to introduce new referents and zero anaphora or more reduced forms were preferred for referent maintenance.

@@

In TİD and many other sign languages, it is possible to use bare nouns as in \ref{ex:2a} as well as fingerspelled nouns as in \ref{ex:2b}. Fingerspelling refers to the use of the manual aphabet to spell all or part of the letters of a word borrowed from a surrounding written language [@kubus2008]. Nouns can also be modified by a prenominal or postnominal extended index finger pointing sign, glossed as IX, functioning as a determiner or a demonstrative as in \ref{ex:2c} [@maclaughlin1997] or by a modifying classifier within the same NP as in \ref{ex:2d} [@frederiksen2016].\footnote{Spoken languages use pronouns, determines and demonstratives where sign languages use a pointing sign, usually glossed as IX, which assumes similar functions (Lillo-Martin and Klima, 1990). In addition, the pointing sign is used to referentially anchor a referent to a location in signing space.}

@@

We tested 29 deaf adult signers, 15 DoD signers with exposure to TİD from birth from deaf caregivers (e.g., parents or siblings), 14 DoH signers who had hearing caregivers and were exposed to TİD between ages 3 and 17. (*M*\textsubscript{Age of acquisition} = 7.7 years, *SD* = 3.3 years). As a result, the criterion to be classified as a DoH signer was to have hearing and non-signing caregivers. All the signers satisfying this criterion were regarded as such.\footnote{Although we did not set a cut-off point for nativeness, all the deaf of hearing participants indicated that they learned TİD after age 3. In order to capture in-group variation among DoH signers, we run an additional supplementary analysis in which we observed very wide credible intervals due to the small group size, rendering the results uninformative. For the analysis, see \ref{section:d}.} All participants indicated that their preferred language of communication was TİD which they used for most contexts. Detailed information about the linguistic and educational background of the participants can be found in \ref{section:a}. 1 DoD signer was excluded from the data analysis because they self-reported to have signing deaf parents but also only used home sign (a more crude form of communication) at home. As a result, we present data from only 14 DoD signers.

@@

Following @berman2013relating, we first identified the clause boundaries in each sentence indicated by the presence of predicates and informative non-manual markers (e.g., head nod). On the second tier, we coded the discourse status for each referent. Having adapted the classification of @gullberg2006, we considered all referents mentioned for the first time as introduced regardless of their syntactic function in the sentence. Only subjects were coded for maintenance and re-introduction. We coded subject referents as maintained only if they had been referred to in the previous clause. To this end, the referents which had been discontinued across one or more sentences were all regarded re-introduced into the discourse. On a third tier, we had the RE type for a single reference with the main categories nominal, pronominal, zero anaphora, and classifier. Under nominal, we identified bare nouns, modified nouns, and fingerspelled nouns. For classifiers, we distinguished among three types of handshapes: WECL, BPCL, and ExtCL. Finally, we had CA, agreement, plain tags for zero anaphora. We were unable to observe any instance of HCLs occurring in isolation (i.e., not part of CA). We should also highlight here that we coded referent status as nominal if the clause included an explicit nominal referent. For example, if constructed action, an index sign, or a classifier preceded or followed its explicitly signed nominal referent, the clause was regarded as having nominal reference (i.e., modified noun). The annotation tiers are presented in Table \ref{tab:tab-2}.

@@

```{=tex}
\begin{table}
\small
\caption{Distribution of zero anaphora by discourse status}
\label{tab:my-table5}
\begin{tabular}{llll}
\hline
                        & Constructed Action & Plain Verb    & Agreement Verb \\ \hline
\textit{Introduced:}    & 1.6\% (17)        & 0.3\% (1)    & 0.5\% (1)      \\
\textit{Maintained:}    & 71.5\% (749)      & 89.3\% (302) & 76.9\% (150)  \\
\textit{Re-introduced:} & 26.8\% (281)      & 10.4\% (35)   & 22.6\% (44)   \\ \hline
\end{tabular}
\end{table}
```
```{r fig:count-plot, echo=FALSE, message=FALSE, cache=FALSE, results='asis', warnings=FALSE, fig.width=4.75, fig.height=3.5, fig.pos="hbt!",fig.cap="Referent counts by Discourse Status (Introduction, Maintanence, Re-introduction), RE Type (Nominal, Pronominal, Classifier, Zero Anaphora), and Participant Group (DoD, DoH)"}
df_narration$ref_type2 <- factor(df_narration$ref_type2,levels = c("NOM", "PRO", "CL", "ZERO"))

@@

For more inference on the data and having pairwise comparisons, we fit a regression model to RE Type using discourse status and acquisition group as predictors. We used the brms package [@burkner2018] in R, with a categorical distribution on the responses and sum contrasts for the predictors Discourse Status (Introduction, Maintenance, Re-introduction) and Participant Group (DoD, DoH). As the overall number of produced pronouns was very little (40 data points), we excluded pronominal use from the following analyses. For the current analysis, we did not define priors ourselves and used the preset uninformed priors. Figure 2[^1] shows the posterior probability distributions where the dot is the median estimate, the thick line is the 50% credible intervals, and the thin line is the 95% credible intervals. There are 3 responses we are considering in this model. They are Classifier, Nominal, and Zero Anaphora. Classifier response is the level that other responses Nominal and Zero Anaphora are compared against.

[^1]: We ran another model where we used the self-reported acquisition time as a predictor with 3 levels 0-3:Early, 4-7:Late1, and 7-above:Late2. However, our model did not converge properly and the credible intervals were very wide spread, yielding the results uninformative. We provide the model results as a plot in \ref{section:d}.

@@

As for the distribution of the zero anaphora, approximately 90% of the plain verbs were used to maintain a previous referent and this makes these constructions least implicit REs used for TİD[^2]. Agreement verbs and CA were the following implicit markers of reference, `r sum(df_narration$GTR1 == "Person agreement verb" & df_narration$Discourse == "Maintenance") / sum(df_narration$GTR1 == "Person agreement verb")` and `r sum(df_narration$GTR1_plot == "CA" & df_narration$Discourse == "Maintenance") / sum(df_narration$GTR1_plot == "CA")` of which were used for maintained contexts, respectively. This contrasts with some of the research [@czubek2017] in which agreement verbs ranked lowest on the scale, indicating that these constructions were more implicit compared to plain verbs. However, there seems to be a common ground for the position of CA markers which have been claimed to rank higher than other markers of zero anaphora as in the present study [@frederiksen2016; @czubek2017; @barbera2009]. In Figure \ref{fig:scale}, we report the distribution of REs in TİD as a function of referent accessibility and compare our accessibility hierarchy with that of [@frederiksen2016] for ASL. In the hierarchies, the leftmost REs (e.g., modified and bare nouns for TİD) are used when the accessibility is low. If the referent is already active in the addressee's mind and its accessibility is high, then the rightmost markers (e.g., agreement and plain verbs for TİD) are selected.

[^2]: As in other sign languages, in TİD, the lexical meaning of signs has an effect on the morphological grouping. For instance, usually (di)transitive agreement verbs denote some sort of physical or metaphorical transfer of an object or abstract notion [@meir1999]. As for plain verbs, both phonology of a sign and its semantics have an effect on morphology. For instance, \textsc{eat} in TİD is signed nearby the mouth and since it needs to remain in that phonological location, it is not suitable for agreement and thus it is regarded as a plain verb. Likewise the experiencer verb \textsc{love} is signed on the torso and as such it does not take part in agreement. These generalizations noted we should also be cautious in labelling a verb as categorially one type or the other. For instance, some intransitive plain verbs like \textsc{fall} or \textsc{jump} in TİD may display spatial person agreement with the single argument in the clause [@gokgoz2020]. See @lourenço2018 also for a similar discussion in Brazilian Sign Language.

```{=tex}
\begin{figure}
\caption{Comparing the present study and Frederiksen and Mayberry (2016) in terms of proposed accessibility hierarchies}
\label{fig:scale}
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

@@

% Text Node
\draw (498,100) node [anchor=north west][inner sep=0.75pt]   [align=left] {\textbf{High}};
% Text Node
\draw (81,100) node [anchor=north west][inner sep=0.75pt]   [align=left] {\textbf{Low}};
% Text Node
\draw (150,88) node [anchor=north west][inner sep=0.75pt]  [font=\fontsize{0.83em}{1em}\selectfont] [align=left] {{\scriptsize NOM}};
% Text Node
\draw (250,88) node [anchor=north west][inner sep=0.75pt]  [font=\fontsize{0.83em}{1em}\selectfont] [align=left] {{\scriptsize ExtCL}};
% Text Node% Text Node
\draw (333,88) node [anchor=north west][inner sep=0.75pt]  [font=\fontsize{0.83em}{1em}\selectfont] [align=left] {{\scriptsize AGR \& CA}};
% Text Node
\draw (445,88) node [anchor=north west][inner sep=0.75pt]  [font=\fontsize{0.83em}{1em}\selectfont] [align=left] {{\scriptsize PLAIN}};
\end{tikzpicture}
\begin{minipage}{\textwidth}
    \footnotesize
    \centering
    Accessibility hierarchy in Frederiksen and Mayberry (2016) for ASL
    \end{minipage}
\end{figure}
```
Both hierarchies illustrated in Figure \ref{fig:scale} treat nominals and ExtCLs as markers of lowly accessibly referents. Likewise, in both hierarchies, as markers of highly accessible referents, different types of zero anaphora markers are further distinguished. Plain verbs rank the lowest on the scales, preceded by agreement verbs and CA. On a similar ground, both scales lack pronouns, which occurred very infrequently in the data. Although @frederiksen2016 did not include other classifier types in the hierarchy, we propose that WECLs and BPCLs must rank higher than zero anaphora but lower than ExtCLs that were mainly used by interlocutors to introduce a referent into the discourse context.

@@

While DoH signers were only partially over-redundant in maintained contexts, they were more so in introduced contexts. In line with our study, a tendency for limited over-redundancy has been suggested for late signing children in DGS [@becker2009] and late signing adults in BSL specifically for the use of CA [@cormier2013]. As for TİD, to our knowledge, there is only one study [@gur2018] that directly aimed at examining age of acquisition effects on adult signers' narrative skills. @gur2018 observed that late signing deaf adults and children set the scene less frequently and used CA less accurately compared to their native counterparts. However, this particular investigation did not present any data on the distribution of REs between two acquisition groups. In the present study, the finding that DoD signers preferred to use null arguments even for the first mention of a referent (`r sum(df_narration$ref_type == "Zero" & df_narration$Discourse == "Introduction")` in total) is surprising given some of the previous literature in the topicality and saliency framework [@cormier2013; @swabey2002]. These research reported very little or no use of zero anaphora by DoD signers for introduced contexts.

>>>>

However, this particular observation is not peculiar to spoken languages. There is an emerging body of literature that reports the distribution of REs in signed narratives [@czubek2017; @ferrara2022; @swabey2002; @frederiksen2016; @perniss2015; @morgan2005; @hodge2019; @ahlgren1994; @garcia_reference_2014; @garcia2018impersonal]. Building on the work by @gundel1993, @swabey2002 demonstrated that, like other languages such as Russian, Chinese, and Japanese, American Sign Language (ASL) signers use bare nouns for introduced and re-introduced discourse contexts whereas zero anaphora is used for referents which are "in-focus" or very accessible to the addressee. Overt REs like pronouns or nouns are disprefered for such referents. @swabey2002 concluded that "native" signers in her study abided by the Gricean maxim of quantity and thus used more economic forms of reference tracking. Similar findings have been reported for German Sign Language (Deutsche Gebärdensprache - DGS) [@perniss2015] and British Sign Language (BSL) [@morgan2005]. It is important to note, however, that this research either collapsed DoD and DoH signers into a single group and labeled them as "native-like" or explicitly compared native deaf signers with late deaf signers (with delayed exposure to a sign language) in terms of narrative competence. Most recently, @ferrara2022 examined corpora including video-recorded narratives from five different sign languages including Irish Sign Language, Finnish Sign Language, Norwegian Sign Language and Swedish Sign Language and investigated how these languages established and maintained referents. Like other observations, this research showed that, across each of these languages, bare nouns were used to introduce new referents and zero anaphora or more reduced forms were preferred for referent maintenance.

@@

In TİD and many other sign languages, it is possible to use bare nouns as in \ref{ex:2a} as well as fingerspelled nouns as in \ref{ex:2b}. Fingerspelling refers to the use of the manual alphabet to spell all or part of the letters of a word borrowed from a surrounding written language [@kubus2008]. Nouns can also be modified by a prenominal or postnominal extended index finger pointing sign, glossed as IX, functioning as a determiner or a demonstrative as in \ref{ex:2c} [@maclaughlin1997] or by a modifying classifier within the same NP as in \ref{ex:2d} [@frederiksen2016].\footnote{Spoken languages use pronouns, determines and demonstratives where sign languages use a pointing sign, usually glossed as IX, which assumes similar functions (Lillo-Martin and Klima, 1990). In addition, the pointing sign is used to referentially anchor a referent to a location in signing space.}

@@

We tested 29 deaf adult signers, 15 DoD signers with exposure to TİD from birth from deaf caregivers (e.g., parents or siblings), 14 DoH signers who had hearing caregivers and were exposed to TİD between ages 3 and 17. (*M*\textsubscript{Age of acquisition} = 7.7 years, *SD* = 3.3 years). As a result, the criterion to be classified as a DoH signer was to have hearing and non-signing caregivers. All the signers satisfying this criterion were regarded as such.\footnote{Although we did not set a cut-off point for nativeness, all the deaf of hearing participants indicated that they learned TİD after age 3. In order to capture in-group variation among DoH signers, we run an additional supplementary analysis in which we observed very wide credible intervals due to the small group size, rendering the results uninformative. For the analysis, see \ref{section:d}.} Detailed information about the linguistic and educational background of the participants can be found in \ref{section:a}.

All participants indicated that their preferred language of communication was TİD which they used for most contexts. 1 DoD signer was excluded from the data analysis because they self-reported to have signing deaf parents but also only used home sign (a more crude form of communication) at home. As a result, we present data from only 14 DoD signers.

@@

Following @berman2013relating, we first identified the clause boundaries in each sentence indicated by the presence of predicates and informative non-manual markers (e.g., head nod). On the second tier, we coded the discourse status for each referent. Having adapted the classification of @gullberg2006, we considered all referents mentioned for the first time as introduced regardless of their syntactic function in the sentence. Only subjects were coded for maintenance and re-introduction. We coded subject referents as maintained only if they had been referred to in the previous clause. To this end, the referents which had been discontinued across one or more sentences were all regarded re-introduced into the discourse. On a third tier, we had the RE type for a single reference with the main categories nominal, pronominal, zero anaphora, and classifier. Under nominal, we identified bare nouns, modified nouns, and fingerspelled nouns. For classifiers, we distinguished among three types of handshapes: WECL, BPCL, and ExtCL. Finally, we had CA[^1], agreement, plain tags for zero anaphora. We were unable to observe any instance of HCLs occurring in isolation (i.e., not part of CA). We should also highlight here that we coded referent status as nominal if the clause included an explicit nominal referent. For example, if constructed action, an index sign, or a classifier preceded or followed its explicitly signed nominal referent, the clause was regarded as having nominal reference (i.e., modified noun). The annotation tiers are presented in Table \ref{tab:tab-2}.

[^1]: Note that CA can also be further subdivided into overt, reduced, and subtle CA, following [@cormier_rethinking_2015]. In overt CA, the signer is "fully in character" and does not use any other lexical or classifier constructions. In reduced CA, the signer can involve a small amount of narration or lexical material while tracking a referent using CA. However, subtle CA refers to cases where the referent is primarily tracked by a non-CA construction (e.g., nominal, pronominal, verbal or classifier constructions) but the signer subtly uses a few CA articulators at the same time (e.g., enacting the eye-gaze of the character). We only coded overt and reduced types as reference tracking by CA, and disregarded the subtle type. We'd also like to acknowledge that mixed CA, or simultaneous tracking of two or multiple references through CA and other tools can be possible [@dudis2004; @liddell2003]. In such cases, as we explain here, we only coded only the subject of a clause for maintenance and re-introduction. If the referent was in subject position and tracked by using CA, we considered this an instance of CA, as well.

@@

```{=tex}
\begin{table}
\small
\caption{Distribution of zero anaphora by discourse status}
\label{tab:my-table5}
\begin{tabular}{llll}
\hline
                        & Constructed Action & Plain Verb    & Agreement Verb \\ \hline
\textit{Introduced:}    & 1.6\% (17)        & 0.3\% (1)    & 0.5\% (1)      \\
\textit{Maintained:}    & 71.5\% (749)      & 89.3\% (302) & 76.9\% (150)  \\
\textit{Re-introduced:} & 26.8\% (281)      & 10.4\% (35)   & 22.6\% (44)   \\ \hline
\end{tabular}
\end{table}
```
```{r fig-count-plot, echo=FALSE, message=FALSE, cache=FALSE, results='asis', warnings=FALSE, fig.width=4.75, fig.height=3.5, fig.pos="hbt!",fig.cap="Referent counts by Discourse Status (Introduction, Maintanence, Re-introduction), RE Type (Nominal, Pronominal, Classifier, Zero Anaphora), and Participant Group (DoD, DoH)"}
df_narration$ref_type2 <- factor(df_narration$ref_type2,levels = c("NOM", "PRO", "CL", "ZERO"))

@@

For more inference on the data and having pairwise comparisons, we fit a regression model to RE Type using discourse status and acquisition group as predictors. We used the brms package [@burkner2018] in R, with a categorical distribution on the responses and sum contrasts for the predictors Discourse Status (Introduction, Maintenance, Re-introduction) and Participant Group (DoD, DoH). As the overall number of produced pronouns was very little (40 data points), we excluded pronominal use from the following analyses. For the current analysis, we did not define priors ourselves and used the preset uninformed priors. Figure 2[^2] shows the posterior probability distributions where the dot is the median estimate, the thick line is the 50% credible intervals, and the thin line is the 95% credible intervals. There are 3 responses we are considering in this model. They are Classifier, Nominal, and Zero Anaphora. Classifier response is the level that other responses Nominal and Zero Anaphora are compared against.

[^2]: We ran another model where we used the self-reported acquisition time as a predictor with 3 levels 0-3:Early, 4-7:Late1, and 7-above:Late2. However, our model did not converge properly and the credible intervals were very wide spread, yielding the results uninformative. We provide the model results as a plot in \ref{section:d}.

@@

As for the distribution of the zero anaphora, approximately 90% of the plain verbs were used to maintain a previous referent and this makes these constructions least implicit REs used for TİD[^3]. Agreement verbs and CA were the following implicit markers of reference, `r sum(df_narration$GTR1 == "Person agreement verb" & df_narration$Discourse == "Maintenance") / sum(df_narration$GTR1 == "Person agreement verb")` and `r sum(df_narration$GTR1_plot == "CA" & df_narration$Discourse == "Maintenance") / sum(df_narration$GTR1_plot == "CA")` of which were used for maintained contexts, respectively. This contrasts with some of the research [@czubek2017] in which agreement verbs ranked lowest on the scale, indicating that these constructions were more implicit compared to plain verbs. However, there seems to be a common ground for the position of CA markers which have been claimed to rank higher than other markers of zero anaphora as in the present study [@frederiksen2016; @czubek2017; @barbera2009]. In Figure \ref{fig-scale}, we report the distribution of REs in TİD as a function of referent accessibility and compare our accessibility hierarchy with that of [@frederiksen2016] for ASL. In the hierarchies, the leftmost REs (e.g., modified and bare nouns for TİD) are used when the accessibility is low. If the referent is already active in the addressee's mind and its accessibility is high, then the rightmost markers (e.g., agreement and plain verbs for TİD) are selected.

[^3]: As in other sign languages, in TİD, the lexical meaning of signs has an effect on the morphological grouping. For instance, usually (di)transitive agreement verbs denote some sort of physical or metaphorical transfer of an object or abstract notion [@meir1999]. As for plain verbs, both phonology of a sign and its semantics have an effect on morphology. For instance, \textsc{eat} in TİD is signed nearby the mouth and since it needs to remain in that phonological location, it is not suitable for agreement and thus it is regarded as a plain verb. Likewise the experiencer verb \textsc{love} is signed on the torso and as such it does not take part in agreement. These generalizations noted we should also be cautious in labelling a verb as categorially one type or the other. For instance, some intransitive plain verbs like \textsc{fall} or \textsc{jump} in TİD may display spatial person agreement with the single argument in the clause [@gokgoz2020]. See @lourenço2018 also for a similar discussion in Brazilian Sign Language.

```{=tex}
\begin{figure}
\caption{Comparing the present study and Frederiksen and Mayberry (2016) in terms of proposed accessibility hierarchies}
\label{fig-scale}
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

@@

% Text Node
\draw (498,100) node [anchor=north west][inner sep=0.75pt]   [align=left] {\textbf{High}};
% Text Node
\draw (81,100) node [anchor=north west][inner sep=0.75pt]   [align=left] {\textbf{Low}};
% Text Node
\draw (150,88) node [anchor=north west][inner sep=0.75pt]  [font=\fontsize{0.83em}{1em}\selectfont] [align=left] {{\scriptsize NOM}};
% Text Node
\draw (250,88) node [anchor=north west][inner sep=0.75pt]  [font=\fontsize{0.83em}{1em}\selectfont] [align=left] {{\scriptsize ExtCL}};
% Text Node% Text Node
\draw (333,88) node [anchor=north west][inner sep=0.75pt]  [font=\fontsize{0.83em}{1em}\selectfont] [align=left] {{\scriptsize AGR \& CA}};
% Text Node
\draw (445,88) node [anchor=north west][inner sep=0.75pt]  [font=\fontsize{0.83em}{1em}\selectfont] [align=left] {{\scriptsize PLAIN}};
\end{tikzpicture}
\begin{minipage}{\textwidth}
    \footnotesize
    \centering
    Accessibility hierarchy in Frederiksen and Mayberry (2016) for ASL
    \end{minipage}
\end{figure}
```
Both hierarchies illustrated in Figure \ref{fig-scale} treat nominals and ExtCLs as markers of lowly accessibly referents. Likewise, in both hierarchies, as markers of highly accessible referents, different types of zero anaphora markers are further distinguished. Plain verbs rank the lowest on the scales, preceded by agreement verbs and CA. On a similar ground, both scales lack pronouns, which occurred very infrequently in the data. Although @frederiksen2016 did not include other classifier types in the hierarchy, we propose that WECLs and BPCLs must rank higher than zero anaphora but lower than ExtCLs that were mainly used by interlocutors to introduce a referent into the discourse context.

@@

While DoH signers were only partially over-redundant in maintained contexts, they were more so in introduced contexts. In line with our study, a tendency for limited over-redundancy has been suggested for late signing children in DGS [@becker2009] and late signing adults in BSL specifically for the use of CA [@cormier2013]. As for TİD, to our knowledge, there is only one study [@gur2018] that directly aimed at examining age of acquisition effects on adult signers' narrative skills. @gur2018 observed that late signing deaf adults and children set the scene less frequently and used CA less accurately compared to their native counterparts. However, this particular investigation did not present any data on the distribution of REs between two acquisition groups. In the present study, the finding that DoD signers preferred to use null arguments even for the first mention of a referent (`r sum(df_narration$ref_type == "Zero" & df_narration$Discourse == "Introduction")` in total) is surprising given some of the previous literature in the topicality and saliency framework [@cormier2013; @swabey2002; @ferrara2022]. These research reported very little or no use of zero anaphora by DoD signers for introduced contexts.
